Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-12-22 SupportingInformation.Rmd
modified

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_soilCN/soilCN_bivfunctionplot.pdf}
\caption[Nonparametric tests against an N-copula null, soil C and N data]{Nonparametric tests for tail dependence and other deviations from N copula structure, for soil C and N data. As described in the main text, the values of the statistics $\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$ and $\Dsq_{l_b,u_b}$ for real data (red crosses) were compared to distributions of their values on 1000 Kendall- or Spearman-preserving N surrogates of the data (blue and green x's show 0.025 and 0.975 quantiles), separately in two comparisons for each of the ranges $(l_b,u_b)=(0,0.1),\ldots,(0.9,1)$. Whenever the red cross was outside the range given by the x's, text at the top of panels indicates the number of surrogate values the real-data value was greater than or less than. For instance, a value $>N$ (respectively, $<N$) means the value of the statistic on real data was greater than (respectively, less than) its value on $N$ surrogates. When the statistic was greater than 975 or less than 975 surrogate values, it indicates significance ($95\%$ confidence level). When $\cor$ or $\Ps$ values (respectively, $\Dsq$ values) were greater than surrogates, it means dependence in that part of the distributions was stronger than (respectively, weaker than) expected from a normal-copula null hypothesis. \label{fig_soilCN_nonparam}}
\end{center}
\end{figure}
<!--***DAN: Shya, can you please adjust this figure and the analogous 3 other figures for the other three bivariate datasets as follows: replace the y-axis label "Partial correlation" with "cor", for consistency with the other y-axis labels-->

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/stat_results/stat_soilCN/soilCN_bivfunctionplot.pdf}
\caption[Nonparametric tests against an N-copula null, soil C and N data]{Nonparametric tests for tail dependence and other deviations from N copula structure, for soil C and N data. As described in the main text, the values of the statistics $\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$ and $\Dsq_{l_b,u_b}$ for real data (red crosses) were compared to distributions of their values on 1000 Kendall- or Spearman-preserving N surrogates of the data (blue and green x's show 0.025 and 0.975 quantiles), separately in two comparisons for each of the ranges $(l_b,u_b)=(0,0.1),\ldots,(0.9,1)$. Whenever the red cross was outside the range given by the x's, text at the top of panels indicates the number of surrogate values the real-data value was greater than or less than. For instance, a value $>N$ (respectively, $<N$) means the value of the statistic on real data was greater than (respectively, less than) its value on $N$ surrogates. When the statistic was greater than 975 or less than 975 surrogate values, it indicates significance ($95\%$ confidence level). When $\cor$ or $\Ps$ values (respectively, $\Dsq$ values) were greater than surrogates, it means dependence in that part of the distributions was stronger than (respectively, weaker than) expected from a normal-copula null hypothesis. \label{fig_soilCN_nonparam}}
\end{center}
\end{figure}
<!--***DAN: Shya, can you please adjust this figure and the analogous 3 other figures for the other three bivariate datasets as follows: replace the y-axis label "Partial correlation" with "cor", for consistency with the other y-axis labels.
***Shya: Done.-->
